Verifying Demonstrations

### 2018-08-20 paper/protocol.tex

\subsection{Verifying the participation count}
\label{ProtocolVerification}

While there are various ways for verifying the participation count, hereafter we will detail the two suggested just after \cref{DefParticipationCount}.
In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
In the second approach, we have a higher trust in specific witnesses.
In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.

\paragraph{Without trusted witnesses}

To verify the participation count for a protest \(P = (\cid, t, l)\) (see \cref{DefProtest}), a verifier must download all the proof shares \(\psh_i =   (\cid, \pid_i, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime   (i)}, l_i, \prf_{\pid_i}, \prf_{\wid_i})\), from the blockchain and verify \(\prf_{\pid_i}\) and \(\prf_{\wid_i}\) and that the interval starting at the latest of \(t_s^{(i)}, t_s^{\prime (i)}\) and ending at the earliest of \(t_e^{(i)}, t_e^{\prime (i)}\) is a subset of \(t\) and that \(l_i\subseteq  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from \cref{DefProofShares} and can thus construct any participation proof \(\prf_{\pid_i, P}\) as in \cref{DefParticipationProof}.

Now, we simply define \(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and then the verifier can compute the participation count \(|\prfs_P^{\str, \theta}|\) as in \cref{DefParticipationCount}.

\paragraph{With trusted witnesses}

For this approach, we must adapt the selection of proof shares from the blockchain by selecting only proof shares issued by witnesses that the verifier trusts.
Thus the verifier must be able to recognize proof shares issued by trusted witnesses, but as \(\prf_\wid\) is currently constructed, this is not possible.
So trusted witnesses must complement their proofs by a digital signature that the verifier can recognize.

When \(S\) only contains proof shares issued by witnesses the verifier trusts, we let \(\str[\prf_{\pid_i, P}] = 1\) and let \(\theta = 1\).
Afterwards, the verifier can compute the participation count \(|\prfs_P^{\str, \theta}|\) as in \cref{DefParticipationCount}.

>>>>

\subsection{Verifying the participation count}%
\label{ProtocolVerification}

While there are various ways for verifying the participation count, hereafter we will detail the two suggested just after \cref{DefParticipationCount}.
In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
In the second approach, we have a higher trust in specific witnesses and no 
trust in others.
In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.

To verify the participation count for a protest \(P = (\cid, t, l)\) (see 
\cref{DefProtest}), a verifier must download all the proof shares \(\psh_i =   
  (\cid, \pid_i, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime   
    (i)}, l_i, \prf_{\pid_i}, \prf_{\wid_i})\), from the blockchain and verify 
\(\prf_{\pid_i}\) and \(\prf_{\wid_i}\) and that the interval starting at the 
latest of \(t_s^{(i)}, t_s^{\prime (i)}\) and ending at the earliest of 
\(t_e^{(i)}, t_e^{\prime (i)}\) is a subset of \(t\) and that \(l_i\subseteq  
  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from 
\cref{DefProofShares} and can thus construct any participation proof 
\(\prf_{\pid_i, P}\) as in \cref{DefParticipationProof}.
Now the verifier can compute the participation count \(|\prfs_P^{\str, 
    \theta}|\) as in \cref{DefParticipationCount}.
It is the strength function \(\str\) that differ in the two cases we give.

In the case \emph{without} trusted witnesses, the verifier simply define 
\(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and set \(\theta\) to our 
desired thresold.

In the case \emph{with} trusted witnesses, each trusted witness must inform the 
verifier of which proof shares that he or she has signed, \eg by giving a list 
of all such proof shares or digitally sign each proof share.
Then the verifier defines \[
  \str[\prf_{\pid_i, P}] = \begin{cases}
    1 & \text{if \(\prf_{\pid_i, P}\) is such a proof share} \\
    0 & \text{otherwise}
  \end{cases}
\] and sets \(\theta = 1\).

### 2018-08-20 paper/system-model.tex

\section{System model}

\include*{protest-model}
\include*{security-properties}

>>>>

\section{Defining and formalizing protest and crowd estimation}%
\label{system-model}

%\subsection{What is \protect\emph{a} protest?}%
%\label{WhatIsAProtest}

%\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital city and repeated every weekend for the duration of a few weeks.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause,%
\label{CauseIsTheCommonDenominator} while the location (or area) considered 
varies over time.

For the rest of the paper, we will refer to the organizer as Alice.
Assume that the objective of Alice is to count everyone who
participated at any time and in any of the
locations~\cite{2016DemonstrationsInSeoul} \sonja{commented out for
  repetition: %\footnote{Note that the objective does not necessarily
              %align with the definition of the police whose interest
              %could be to determine the maximum crowd at any point in
              %time to deploy enough personnel for crowd-control.
}.
% cause identifier
Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.

% protest
% subprotest

\begin{definition}[Subprotest, Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in \ZZ_{2^\lambda}\) is the identifier of the cause of the protest,
  \(t \subseteq \RR\) is a time period and \(l \subseteq \RR^2\) is the location (the topological connectedness is not necessary).
  A \emph{protest} is a set of subprotests sharing the same \(\cid\).
\end{definition}

The protests described in the previous examples can be captured using this definition by decomposing them up into subprotests.
Each subprotest will then be encapsulated by our definition and to estimate the total participation to the protest we can just sum up the estimates obtained.
Similarly for marches, the marching path can be divided into subprotests with locations (or areas) that slightly overlap.

\emph{Formalizing the notion of crowd estimation.} 
Each participant who wants to be counted must submit a \emph{participation proof}.
The proof must be associated with the protest (\ie its identifier \(cid\)), and its time and location must coincide with one of the subprotests.

Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the risk of inflation.
Note that a participant of a protest can take the role of a protester but also act as witness for other protesters.
%Seb: the sentence below is not very clear, it should be rephrased to make it clearer
The participation proof and its proof shares are stored in a set, as there should be only unique proof shares.

% proof share
% proof shares
% protester identifier
% witness identifier

\begin{definition}[Proof share]%
  \label{DefProofShare}\label{DefProofShares}
  A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: 
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
  We say that \(\psh\) is part of a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
  \(\psh \sqsubseteq \sprtst\).
  We define \(\pshs\) as the set of all proof shares.
\end{definition}

A subset of the proof shares forms a participation proof for a protester.

% proof
% proofs

\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  A \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
  \begin{multline}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
  \end{multline}
  of all proof shares with the same protester and protest identifiers, witnessing time interval \(t\) and location \(l\) within those of the protest.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

% strength
\NewFunction{\str}{\varsigma}

We can now define the participation count as follows.
\begin{definition}[Participation count]%
  \label{DefParticipationCount}
  We define the \emph{participation count} of a protest \(\prtst\) (as in \cref{DefParticipationProof}) as the cardinality 
  \(|\prfs_{P}^{\str,\theta}|\) of the set of participation proofs \[
    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,P} \in \prfs \mid
      \str(\prf_{i,P})\geq \theta \right\}
  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a 
  threshold \(\theta\).
\end{definition}

The strength function \(\str\) can be used to regulate the trust in the participation count estimated.
One example would be for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
%Seb: we should define clearly the different type of witnesses (for instance unique and trusted witnesses)
Another possibility would be to also have a particular type of witness, called trusted witness, participating in the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the strength function could be defined with respect to the number of proof shares issued by trusted witnesses and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.
